Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2021-01-28 Scripts/Initial_Analysis.Rmd
ready to run for p90

```{r Proportion_control_panel, eval = T, echo = F}

@@

GetTransIndex <- function(taxon_key,
                          year,
                          Hist_y,
                          data_type = "Catch",
                          path,
                          ensemble_list,
                          Neighbours,
                          eez_centroid,
                          Plot = F){
  t_start <- Sys.time()
  print("Starting Step One")
    # First step
    # Call Get centroids fucntion for centroids data per ensemble

  Step_one <- bind_rows(
      lapply(ensemble_list,
             GetCentroids,
             taxon_key = taxon_key, # for testing
             year = year_df$year,
             data_type = data_type,
             Neighbours = Neighbours,
             eez_centroid = eez_centroid
             )
    )

@@

```{r Emerging_routine, eval = F, echo = F}

####_______________________ ####
# Estimating year of eergence
####_______________________ ####
n_cores <- 24
t_start <- Sys.time()

@@

    Emerging_result <- bind_rows(
      mclapply(spp_list,
               GetTransIndex,
               year = year_df$year,
               Hist_y = Historic_year,
               data_type = "Abd",
               ensemble_list = ensemble_list,
               Neighbours = Neighbours,
               eez_centroid = eez_centroid,
               Plot = F
      )
    )

@@

```{r get_env_data, eval = T, echo = T}

@@

```{r ToE_generals,  eval = T, echo = T}

@@

```{r Time_lapse_data,  eval = T, echo = T}

@@

```{r Time_lapse_plot, eval = T, echo = F}

@@

```{r emergence_map, eval = T}

@@

```{r data_loading, eval = T, echo = F}

@@

```{r data_analysis, eval = T, echo = F}

@@

```{r time_emergence_map,  eval = T, echo = T}

@@

```{r histo,  eval = T, echo = T}

@@

```{r temp_plot, eval = T, echo = T}

@@

```{r Scatter_plot,  eval = T, echo = T}

>>>>

```{r Proportion_control_panel, eval = F, echo = F}

@@

GetTransIndex <- function(taxon_key,
                          year,
                          Hist_y,
                          data_type = "Catch",
                          path,
                          ensemble_list,
                          Neighbours,
                          eez_centroid,
                          p = NA,
                          Plot = F){
  t_start <- Sys.time()
  print("Starting Step One")
    # First step
    # Call Get centroids fucntion for centroids data per ensemble

  Step_one <- bind_rows(
      lapply(ensemble_list,
             GetCentroids,
             taxon_key = taxon_key, # for testing
             year = year_df$year,
             data_type = data_type,
             Neighbours = Neighbours,
             eez_centroid = eez_centroid,
             p = p
             )
    )

@@

```{r Emerging_routine, eval = T, echo = F}

####_______________________ ####
# Estimating year of eergence
####_______________________ ####
# n_cores <- 24
t_start <- Sys.time()

@@

    Emerging_result <- bind_rows(
      mclapply(spp_list,
               GetTransIndex,
               year = year_df$year,
               Hist_y = Historic_year,
               data_type = "Abd",
               ensemble_list = ensemble_list,
               Neighbours = Neighbours,
               eez_centroid = eez_centroid,
               p = 0.90,
               Plot = F
      )
    )

@@

```{r get_env_data, eval = F, echo = T}

@@

```{r ToE_generals,  eval = F, echo = T}

@@

```{r Time_lapse_data,  eval = F, echo = T}

@@

```{r Time_lapse_plot, eval = F, echo = F}

@@

```{r emergence_map, eval = F}

@@

```{r data_loading, eval = F, echo = F}

@@

```{r data_analysis, eval = F, echo = F}

@@

```{r time_emergence_map,  eval = F, echo = T}

@@

```{r histo,  eval = F, echo = T}

@@

```{r temp_plot, eval = F, echo = T}

@@

```{r Scatter_plot,  eval = F, echo = T}
